Mood increases during video game play: A naturalistic observational case study of PowerWash Simulator

### 2023-09-04 ms.qmd
Estimate full model

$$
\begin{align*}
\text{mood}_{ijk} &\sim \text{CensNormal}(\eta_{ijk}, \kappa_{ij}, 0, 1), \\
\eta_{ijk} &= (\alpha_0 + \beta_{0j})\text{pre}_{ijk} +
  (\alpha_1 + \beta_{1j})\text{post}_{ijk} +
  \gamma_{0k}, \\
log(\kappa_{ij}) &= \alpha_2 + \beta_{2j}, \\
\begin{bmatrix} \alpha_0 \\ \alpha_1 \\ \alpha_2 \end{bmatrix} &\sim 
  \text{MVN}\left(\begin{bmatrix} 0 \\ 0 \\ 0 \end{bmatrix}, 
  \begin{bmatrix} 
    \tau_{\alpha_0} &\rho_{{\alpha_0}{\alpha_1}} &\rho_{{\alpha_0}{\alpha_2}} \\ 
    \rho_{{\alpha_0}{\alpha_1}} &\tau_{\alpha_1} &\rho_{{\alpha_1}{\alpha_2}} \\ 
    \rho_{{\alpha_0}{\alpha_2}} &\rho_{{\alpha_1}{\alpha_2}} &\tau_{\alpha_2} 
  \end{bmatrix}\right), \\
  \gamma_0 &\sim \text{Normal}(0, \tau_{\gamma_0})
\end{align*}
$$

@@

set.seed(999)
dat_snip <- dat |>
  filter(pid %in% sample(unique(dat$pid), 100))

@@

fit <- brm(
  model,
  data = dat_snip,
  silent = 0,
  threads = 2,
  iter = 1500,
  control = list(adapt_delta = .9),
  file = "models/brm-pre-post-location-scale"
)
summary(fit, prior = TRUE)
```

>>>>

$$
\begin{align*}
\text{mood}_{ijk} &\sim \text{CensNormal}(\eta_{ijk}, \kappa_{ij}, 0, 1), \\
\eta_{ijk} &= (\alpha_0 + \beta_{0j})\text{pre}_{ijk} +
  (\alpha_1 + \beta_{1j})\text{post}_{ijk} +
  \gamma_{0k}, \\
log(\kappa_{ij}) &= \alpha_2 + \beta_{2j}, \\
\begin{bmatrix} \alpha_0 \\ \alpha_1 \\ \alpha_2 \end{bmatrix} &\sim 
  \text{MVN}\left(\begin{bmatrix} 0 \\ 0 \\ 0 \end{bmatrix}, 
  \begin{bmatrix} 
    \tau_{\alpha_0} &\rho_{{\alpha_0}{\alpha_1}} &\rho_{{\alpha_0}{\alpha_2}} \\ 
    \rho_{{\alpha_0}{\alpha_1}} &\tau_{\alpha_1} &\rho_{{\alpha_1}{\alpha_2}} \\ 
    \rho_{{\alpha_0}{\alpha_2}} &\rho_{{\alpha_1}{\alpha_2}} &\tau_{\alpha_2} 
  \end{bmatrix}\right), \\
  \gamma_0 &\sim \text{Normal}(0, \tau_{\gamma_0}).
\end{align*}
$$

@@

@@

fit <- brm(
  model,
  data = dat,
  silent = 0,
  threads = 2,
  iter = 100,
  control = list(adapt_delta = .9),
  file = "models/brm-pre-post-location-scale"
)
summary(fit, prior = TRUE)
```
